\papertitle

### 2017-03-16 paper/paper.tex
Compare error on each paramater for 2 components.

\usepackage{hyphenat}
\hyphenation{spher-oidal}

@@

@@

\begin{abstract}
TODO
\end{abstract}

\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}

\begin{figure*}[ht]
    \centerline{\includegraphics[width=5in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
phase sinusoids averaged over 1000 trials. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}

\begin{figure*}[ht]
    \centerline{\includegraphics[width=5in]{{comp_offset_chirp_est_err}.eps}}
\caption{\label{fig:mixwincomp}}
\end{figure*}

@@

\cite{hamilton2012comparisons} gives a comprehensive evaluation of the signal
derivative methods. In \cite{robel2002estimating} the extent to which two
components in mixture can corrupt estimations of the frequency slope
($\Im{a_{0,2}}$ and $\Im{a_{1,2}}$) is investigated in the context of the
reassignment method, a related technique, but the corruption of the other
parameters is not considered.

The signal-derivatives technique we will consider is the
Distribution Derivative Method for its convenience: the technique does not
require computing derivatives of the signal to be analysed. It does, however, require a
$p$ times differentiable analysis window where $p+1$ is the order of the
phase polynomial to be estimated.

@@

To estimate $a_0$ we write the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\]
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\]
The inner-product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

@@

We examine how the mixture model influences the estimation of the $a_{i,j}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0
    \\ = 
    \sum_{i=1}^{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}

In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

@@

\section{Differentiable approximations to windows}

A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

@@

\section{Continuous window design example}
\label{sec:designexample}

As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

In \cite{verma1996digital} it was shown how to construct digital prolate
spheroidal windows under parameters $N$, the window length in samples, and a
parameter $W$. We chose $N=512$ based on the window length chosen in
\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
at a resolution of $0.001$. The window with the closest 3db bandwidth to the
4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
shown in Fig.~\ref{fig:dpw}. We see that
this window's asymptotic roll-off is 6 dB per octave and is therefore has a
discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
$N/8$ to find the best approximation to the digital prolate window's main lobe
using a small number of cosines. The $M$ giving the best approximation was $5$.
The magnitude response of the approximation is shown in
Fig.~\ref{fig:dpw}.  We see that we obtain a lower highest sidelobe
level than the Nuttall and Prolate windows by slightly sarificing the narrowness
of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
the rolloff of the window is 18 dB per octave because it is once-differentiable
at all points in its domain.

@@

To compare the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized random sinusoids using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and parameters choosen from uniform distributions justified in
\cite{betser2009sinusoidal}. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, the three atoms whose inner products were greatest were used in
the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
lower sidelobes exhibit the lowest possible error variance at the sacrifice of
some estimator efficiency.

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
uniform distributions specified in \cite{betser2009sinusoidal}. One of the two
components was scaled to give a desired signal power ratio with the other
component. The parameters of both components were estimated and the total
squared estimation error for all the parameters was recorded. In
Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation error
for components having similar signal power. This is to be expected as there will
be less masking of the weaker signal in these scenarios. The estimation error is
large when the atoms containing the most signal energy for each component are
not greatly separated in frequency. This is due to the convolution of the
Fourier transform of the window with the signal, and agrees with what was
predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger main lobe exhibit
a larger `radius' in which the error of the parameter estimation will be high.
However, for signals where local inner product maxima are from atoms sufficiently
separated in frequency, windows with lower sidelobes are better at attenuating
the other component and for these the estimation error is lowest.

@@

\section{Acknowledgments}

@@

\section{Appendix}

>>>>

\usepackage{hyphenat}
\hyphenation{spher-oidal}
%\hyphenation{amp-li-tude}
%\hyphenation{mod-u-lat-ed}

@@

\input{ddm_snr_win_comp_defs.txt}
\input{comp_offset_chirp_est_err_defs.txt}

@@

\begin{abstract}
    The accuracy of the Distribution Derivative Method (DDM)
    \cite{betser2009sinusoidal} is evaluated on mixtures of chirp signals. It is
    shown that accurate estimation can be obtained when the sets of atoms for
    which the inner product is large are disjoint.  This amounts to designing
    atoms with windows whose Fourier transform exhibits low sidelobes but which
    are once-differentiable in the time-domain. A technique for designing
    once-differentiable approximations to windows is presented and the accuracy
    of these windows in estimating the parameters of chirps in mixture is
    evaluated.
\end{abstract}

@@

\cite{hamilton2012comparisons} gives a comprehensive evaluation of the signal
derivative methods. In \cite{robel2002estimating} the extent to which two
components in mixture can corrupt estimations of the frequency slope
($\Im\{a_{0,2}\}$ and $\Im\{a_{1,2}\}$) is investigated in the context of the
reassignment method, a related technique, but the corruption of the other
parameters is not considered.

The signal-derivatives technique we will consider is the
DDM for its convenience: the technique does not
require computing derivatives of the signal to be analysed. It does, however, require a
once-differentiable analysis window.

@@

To estimate $a_0$ we write the signal we are analysing as
\[
    x(t) = \exp(a_0) \gamma(t) + \epsilon (t)
\]
where $\epsilon (t)$ is the error signal, the part of the signal that is not explained
by our model, and $\gamma (t)$ is the part of the signal
whose coefficients have already been estimated, i.e.,
\[
    \gamma(t) = \exp \left( \sum_{j=1}^{Q} a_j t^{j} \right)
\]
Computing the inner product $\left\langle x , \gamma \right\rangle$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \left\langle \exp(a_0) \gamma , \gamma \right\rangle + 
        \left\langle \epsilon , \gamma \right\rangle
\]
The inner-product between $\epsilon$ and $\gamma$ is $0$, by the orthogonality
principle \cite[ch.~12]{kay1993fundamentals}. Furthermore, because $\exp(a_0)$ does not
depend on $t$, we have
\[
    \left\langle x , \gamma \right\rangle
    =
    \exp(a_0) \left\langle \gamma , \gamma \right\rangle
\]
so we can estimate $a_0$ as
\begin{equation}
    \label{eq:ddmesta0}
    a_0 = \log \left( \left\langle x , \gamma \right\rangle \right)
        - \log \left( \left\langle \gamma , \gamma \right\rangle \right)
\end{equation}

@@

We examine how the mixture model influences the estimation of the $a_{i,j}$ in
Eq.~\ref{eq:polyphaseexpmix}.
Consider a mixture of $P$ components.
If we define the weighted signal sum
%
\[
    g(t) = \sum_{i=1}^{P} x_{i}(t) \overline{\psi}(t) = \sum_{i=1}^{P} f_{i}(t)
\]
%
and substitute $g$ for $f$ in Eq.~\ref{eq:ddm:weighted:sig:derivative} we obtain
%
\begin{multline}
    \label{eq:mixest}
    \sum_{i=1}^{P} \int_{-\frac{L_{t}}{2}}^{\frac{L_{t}}{2}} \frac{df_{i}}{dt}(t) =
    0
    \\ = 
    \sum_{i=1}^{P}
    \sum_{j=1}^{Q} j a_{i,j} 
    \left\langle \mathcal{T}^{j-1} x_i , \overline{\psi} \right\rangle
     + \left\langle x_i, \frac{d\overline{\psi}}{dt} \right\rangle
\end{multline}
%
From this we see if $\left\langle \mathcal{T}^{j-1} x_i , \overline{\psi}_{r}
\right\rangle$ and $\left\langle x_i, \frac{d\overline{\psi_{r}}}{dt} \right\rangle$
are small for all but $i = i^{\ast}$ and a subset of $R$ atoms, we
can simply estimate the parameters $a_{i^{\ast},j}$ using
\[
    \sum_{j=1}^{Q} j a_{{i^{\ast}},j} 
    \left\langle \mathcal{T}^{j-1} x_{i^{\ast}} , \overline{\psi}_{r} \right\rangle
    = -\left\langle x_{i^{\ast}}, \frac{d\overline{\psi}_{r}}{dn} \right\rangle
\]
for $1 \leq r \leq R$. To compute $a_{i^{\ast},0}$ we simply use
\[
    \gamma_{i^{\ast}}(t) = \exp \left( \sum_{j=1}^{Q} a_{i^{\ast},j} t^{j} \right)
\]
in place of $\gamma$ in Eq.~\ref{eq:ddmesta0}.

\section{Designing the $\psi_{r}$}
\label{sec:designingatoms}
%
\begin{figure*}[t]
    \centerline{\includegraphics[width=7in]{{search_dpw_bw_m}.eps}}
\caption{\label{fig:dpw} Comparing the main-lobe and asymptotic power
spectrum characteristics of the continuous 4-term Nuttall window, the digital
prolate window with $W=0.008$, and the continuous approximation to the digital
prolate window.}
\end{figure*}
%
In practice, an approximation of Eq.~\ref{eq:ddm:inner:prod:def} is evaluated using
the discrete Fourier transform (DFT) on a signal $x$ that is properly sampled
and so can be evaluated at a finite number of points $nT$ with $n \in [0,N-1]$ and
$T$ the sample period in seconds. In this way, the atoms $\psi_{\omega}(t)$ chosen
are the products of the elements of the Fourier basis and an appropriately
chosen window $w$ that is once differentiable and finite, i.e.,
%
\[
    \psi_{\omega}(t) = w(t) \exp(-\sqrt{-1} \omega t)
\]
%
Defining $N = \frac{L_{t}}{T}$ and $\omega = 2
\pi \frac{r}{N}$, the approximate
inner product is then
%
\[
    \left\langle x , \psi_{\omega} \right\rangle \approx 
    \sum_{n=0}^{N-1} x(Tn) w(Tn) \exp(-2 \pi \sqrt{-1} r \frac{n}{N}) 
\]
%
i.e., the definition of the DFT of a windowed signal.%
\footnote{%
    Notice however that this is an approximation of the inner product and should
    not be interpreted as yielding the Fourier series coefficients of a properly
    sampled signal $x$ periodic in $L_{t}$. This means that other
    evaluations of the inner product that yield more accurate results are
    possible. For example, the analytic solution is possible if $x$ is assumed
    zero outside of $[-\frac{L_{t}}{2},\frac{L_{t}}{2}]$ (the $\psi$ are in
    general analytic).  In this case the samples of $x$ are convolved with the
    appropriate interpolating sinc functions and the integral of this function's
    product with $\psi$ is evaluated.
}%
The DFT is readily interpreted as a bank of bandpass filters centred at
normalized frequencies%
\footnote{%
In this article as in much of the literature on signal processing the index $r$
of the Fourier basis element corresponding to the frequency $\omega_{r} = 2 \pi
\frac{r}{N}$ will be referred to as its bin number.
}
$\frac{r}{N}$ and with frequency response described by the Fourier transform of
modulated $w$ \cite{allen1977unified}. Therefore choosing $\psi$ amounts to a
filter design problem under the constraints that the impulse response of the
filter be differentiable in $t$ and finite. To minimize the influence of all but
one component, granted the components's energy concentrations are sufficiently
separated in frequency, we desire impulse responses whose magnitude response
gives maximum out-of-band rejection or equivalently, windows whose Fourier
transform exhibits the lowest sidelobes.

@@

\section{Differentiable approximations to windows}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{ddm_snr_win_comp}.eps}}
\caption{\label{fig:snrwincomp} The estimation variance of random polynomial
    phase sinusoids averaged over $K_{1}=\Ksnr{}$ trials using atoms generated from
    various windows. \textit{C} is the Cram\'{e}r-Rao
lower bound, \textit{N3} and \textit{N4} are the 3- and 4-cosine-term continuous
Nuttall windows, \textit{H} is the Hann window, and \textit{P5} is the continous
5-cosine-term approximation to a digital prolate window as described in
Sec.~\ref{sec:designexample}.}
\end{figure*}
%
A differentiable approximation to a symmetrical window can be designed in a
straightforward way. In \cite{harris1978use} and \cite{rabiner1970approach} it
is shown how to design optimal windows of length $N$ samples using a linear
combination of $M$ harmonically related cosines
\begin{equation}
    w(n) = \sum_{k=0}^{M-1} b_{k} \cos (2 \pi k \frac{n}{N})
\mathcal{R}(\frac{n}{N})
\end{equation}
where $\mathcal{R}$ is the \textit{rectangle function}. This function is
discontinuous
at $n = \frac{\pm N}{2}$, and therefore not differentiable there, unless
\[
\sum_{k=0}^{M-1} b_{k} \cos ( \pm \pi k ) = 0
\]

@@

\section{A continuous window design example}
\label{sec:designexample}
%
\begin{figure*}[ht]
    \centerline{\includegraphics[width=7in]{{comp_offset_chirp_est_err_params}.eps}}
\caption{\label{fig:mixwincomp} The mean squared estimation error for each
    parameter in an analysis of two components in mixture. A set of
    $K_{2}=\Koffset{}$ chirps was synthesized and each unique pair used for
    maximum bin differences $0 \leq d < \Doffset{}$. The signal power ratio
    between components is indicated using shades of grey: lighter shades
    indicate a ratio closer to $1$. The ratio in decibels is indicated in the
    plot legend. The names indicate the windows used to generate the atoms for
    estimation: \textit{N3} and \textit{N4} are the 3- and 4-cosine-term
    continuous Nuttall windows, \textit{H} is the Hann window, and \textit{P5}
is the continous 5-cosine-term approximation to a digital prolate window as
described in Sec.~\ref{sec:designexample}.}
\end{figure*}
%
As a design example we show how to create a continuous approximation of a digital
prolate spheroidal window.

@@

In \cite{verma1996digital} it was shown how to construct digital prolate
spheroidal windows under parameters $N$, the window length in samples, and a
parameter $W$. We chose $N=512$ based on the window length chosen in
\cite{betser2009sinusoidal} for ease of comparison. Its $W$ parameter's value
was chosen by synthesizing windows with $W$ ranging between $0.005$ and $0.010$
at a resolution of $0.001$. The window with the closest 3db bandwidth to the
4-term Nuttall window was obtained with $W=0.008$. Its magnitude response is
shown in Fig.~\ref{fig:dpw}. We see that
this window's asymptotic falloff is 6 dB per octave and therefore has a
discontinuity somewhere in its domain \cite{nuttall1981some}. We designed an approximate
window using Eq.~\ref{eq:searchcontwinprogram} for $M$ varying between $2$ and
$N/8$ to find the best approximation to the digital prolate window's main lobe
using a small number of cosines. The $M$ giving the best approximation was $5$.
The magnitude response of the approximation is shown in
Fig.~\ref{fig:dpw}.  We see that we obtain a lower highest sidelobe
level than the Nuttall and Prolate windows by slightly sarificing the narrowness
of the main lobe. Furthermore in Fig.~\ref{fig:dpw} we observe that
the falloff of the window is 18 dB per octave because it is once-differentiable
at all points in its domain.

@@

To compare the average estimation error variance with the
theoretical minimum given by the Cram\'{e}r-Rao bound we synthesized $K_{1}$ random
chirps using Eq.~\ref{eq:polyphaseexp}
with $Q=2$ and parameters choosen from uniform distributions justified in
\cite{betser2009sinusoidal}. The original Hann window,
the windows proposed by Nuttall and the new digital prolate based window were
used to synthesize the atoms as described in Sec.~\ref{sec:designingatoms} and
their estimation error variance was compared (see
Fig.~\ref{fig:snrwincomp}). After performing the DFT to obtain inner products
with the atoms, the three atoms whose inner products were greatest were used in
the estimations, i.e., $R=3$ in Eq.~\ref{eq:ddmsyseq}. We see that windows with
lower sidelobes exhibit the lowest possible error variance at the sacrifice of
some estimator efficiency.

To evaluate the performance of the various windows when estimating the
parameters of components in mixture we synthesized signals using
Eq.~\ref{eq:polyphaseexpmix} with $P=2$ and $Q=2$ and parameters chosen from the
uniform distributions specified in \cite{betser2009sinusoidal}. A set
$\mathcal{C}$ of $K_{2}$ components was synthesized. The atom $r^{\ast}$ for which
the inner product was maximized was determined for each unmixed chirp and the
chirp was modulated by $\exp(-2\pi \frac{r^{\ast} n}{N}\sqrt{-1})$ for $0 \leq n
< N$ in order to move this maximum to $r=0$. Then for each desired difference
$d$ between maxima in bins, with $0 \leq d < D$, two unique chirps were
selected from $\mathcal{C}$ and one chirp was modulated by $\exp(2\pi
\frac{d n}{N}\sqrt{-1})$ for $0 \leq n < N$ in order to give the desired difference in
maxima. This component was also scaled by a constant to give a desired signal
power ratio with the other component. The parameters of both components were
estimated using the bins surrounding $r=0$ and $r=d$ for each component
respectively and the squared estimation error for each parameter was summed and divided
by $K_{2}(K_{2}-1)$ to give the averaged squared estimation error for each
parameter at each difference $d$.

In Fig.~\ref{fig:mixwincomp} we see that there is generally less estimation
error for components having similar signal power. This is to be expected as
there will be less masking of the weaker signal in these scenarios.  The
estimation error is large when the atoms containing the most signal energy for
each component are not greatly separated in frequency. This is due to the
convolution of the Fourier transform of the window with the signal, and agrees
with what was predicted by Eq.~\ref{eq:mixest}: indeed windows with a larger
main lobe exhibit a larger `radius' in which the error of the parameter
estimation will be high.  However, for signals where local inner product maxima
are from atoms sufficiently separated in frequency, windows with lower sidelobes
are better at attenuating the other component and for these the estimation error
is lowest.

@@

Motivated by the need to analyse mixtures of frequency- and
am\-pli\-tude-mod\-u\-lat\-ed
sinusoids (Eq.\ref{eq:polyphaseexpmix}), we have shown that the DDM can be
employed under a single-component
assumption when components have roughly disjoint sets of atoms for which their
inner products take on large values. This indicates the need for windows whose
Fourier transform exhibits low sidelobes. We developed windows whose sidelobes
are minimized while remaining everywhere once-differentiable: a requirement to
generate valid atoms for the DDM. These windows were shown to improve parameter
estimation of $P=1$ and $P=2$ components in mixture, granted the components
exhibited reasonable separation in frequency between the atoms for which the
inner product was maximized.

Further work should evaluate these windows on sinusoids of different orders,
i.e., $Q \gg 1$. Optimal main-lobe widths for windows should be determined
depending on the separation of local maxima in the power spectrum. It should
also be determined if these windows improve the modeling of real-world acoustic
signals.

%\section{Acknowledgments}

@@

%\section{Appendix}
